### 2025-03-06 ms.qmd
updates

## Results
```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_complete.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(k in 1:length(hormone)){
  for(l in 1:length(temperature)){
    n_list[[paste(hormone[k], temperature[l], sep = "_")]] <- sample(hormone[k], temperature[l])
  }
}
```

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# 
# df got from data_process.R
#
fchoice <- bf(choice_slope_mean + choice_slope_se ~ cort*temp)
ferrors <- bf(errors_slope_mean + errors_slope_se ~ cort*temp)
fROS <- bf(ROS ~ Mit_density + cort*temp)
#
refit <- FALSE
if(refit==TRUE){
  # Choice
  model_choice_2 <- brm(fchoice + fROS,
                data = clean_df,
                family = gaussian,
                chains = 4, cores = 4, iter = 8000, warmup = 2000, 
                control = list(adapt_delta = 0.99, max_treedepth = 12))
  # Errors
  model_errors_2 <- brm(ferrors + fROS,
                data = clean_df,
                family = gaussian,
                chains = 4, cores = 4, iter = 8000, warmup = 2000,
                control = list(adapt_delta = 0.99, max_treedepth = 12))
  # Write the models to two files
  saveRDS(model_choice_2, file = paste0(here("output/models/model_choice_2.rds")))
  saveRDS(model_errors_2, file = paste0(here("output/models/model_errors_2.rds")))
  } else {
    # Read the model from a file
    model_choice_2 <- readRDS(file = paste0(here("output/models/model_choice_2.rds")))
    model_errors_2 <- readRDS(file = paste0(here("output/models/model_errors_2.rds")))
} 
post_gen <- as_draws_df(model_errors_2)
write.csv(post_gen, file= "./output/Checking/post_gen.csv")
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```

```{r, tbl-data}
#| label: tbl-data

@@

```{r, fig-learning}
#| label: fig-learning
#| fig.cap: "Results for L. delicata (A,B) and L. guichenoti (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
####### A) Probability of choosing correct figure
## A.1) Get the df with the estimated probability of choosing the correct feeder first over trials (using learning_df from data_process.R)
# Get the df for the intercepts
post_choice_intercept <- tidy_post_df("choice", "intercept")
# Merge slope and intercept dfs for choice 
learning_df_prob <- merge(learning_df, post_choice_intercept, by = "lizard_id", all = TRUE)
# Create a vector with treatments
# Create new matrix and new dfs
treat_matrix <- matrix(NA, nrow = 20, ncol = 40)
fig_df <- data.frame()
# Loop through treatments
for(t in treatments){
  if(t == "CORT-Cold"){
    df <- learning_df_prob %>%
      filter(cort=="CORT", temp=="Cold") %>%
      data.frame()
  } else if(t == "Control-Cold"){
    df <- learning_df_prob %>%
      filter(cort=="Control", temp=="Cold") %>%
      data.frame()
  } else if(t == "CORT-Hot"){
    df <- learning_df_prob %>%
      filter(cort=="CORT", temp=="Hot") %>%
      data.frame()
  } else if(t == "Control-Hot"){
    df <- learning_df_prob %>%
      filter(cort=="Control", temp=="Hot") %>%
      data.frame()
  } else {
    stop("loop wrong")
  }
  # Variables selected
  m <- df$choice_slope__mean
  u <- df$choice_intercept__mean
  # Loop per treatment
  num_individuals <- length(u)
  for(x in 0:40){
    for(j in 1:num_individuals){
      value <- exp(u[j] + m[j] * x) / (1 + exp(u[j] + m[j] * x))
      treat_matrix[j, x] <- value
    }
  }
  treat_df <- as.data.frame(treat_matrix)
  colnames(treat_df) <- paste0("X", 1:40)  # Adjust column names
  treat_df <- gather(treat_df, key = "Trial", value = "Value")  # Reshape data frame
  treat_df$Treatment <- t
  fig_df <- rbind(fig_df, treat_df)
}
# Transform the database for better use
fig_choice_df <- fig_df %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)/sqrt(length(Value))
    ) %>%
  ungroup() %>%
  mutate(
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
data.frame()
## A.2) Make the plot for the probability of choosing the correct feeder first over trials
fig_prob_choice <- ggplot(fig_choice_df, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("CORT-Cold"="#00008B", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +
  geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +
  theme_classic() +
  labs(y = "Predicted probability of correct choice", x = "Trial") +
  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
  theme(
    axis.title = element_text(size = 12, family = "Times"),
    axis.text = element_text(size = 10, family = "Times"),
    legend.position = "none"
## A.3) Make the the plot for the mean slope per treatment using the probability of choosing the correct feeder
fig_slope_choice <- plot_slopes("choice")
## A.4) Combine plots of probability and slopes to have the "choice" figure
fig_results_choice <- plot_grid(fig_prob_choice, fig_slope_choice, nrow = 1) 
ggsave("./output/figures/fig_results_choice.png", plot=fig_results_choice, width = 25, height = 15, units = "cm", dpi = 600)
####### B) Errors figure
## B.1) Plot the errors using data_spal
errors_df <- data_spal %>%
  mutate(Treatment = paste(cort, temp, sep = "-")) %>%
    mutate(Treatment = factor(Treatment,
      levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
    )) %>%
  group_by(day, Treatment) %>%
  summarise(
    mean_errors = mean(errors, na.rm = TRUE),
    sd_errors = sd(errors, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  data.frame()
fig_errors <- ggplot(errors_df, aes(x = day, y = mean_errors, color = Treatment, fill = Treatment)) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1, alpha = 0.075) +
  scale_color_manual(values = c("CORT-Cold" = "#00008B", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  scale_fill_manual(values = c("CORT-Cold" = "darkblue", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  theme_classic() +
  labs(y = "Mean amount of errors made", x = "Trial") +
  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
  theme(
    axis.title = element_text(size = 12, family = "Times"),
    axis.text = element_text(size = 10, family = "Times"),
    legend.position = "none"
## B.2) Make the the plot for the mean slope per treatment using the probability of choosing the correct feeder
fig_slope_errors <- plot_slopes("errors")
## B.3) Combine plots of probability and slopes to have the "choice" figure
fig_results_errors <- plot_grid(fig_errors, fig_slope_errors, nrow = 1) 
ggsave("./output/figures/fig_results_errors.png", plot=fig_results_errors, width = 25, height = 15, units = "cm", dpi = 600)

@@

# Suplementary Material
#### Results of preliminary models

```{r, models_preliminary}
#| label: models_preliminary
# Fitting preliminary models to see if sex and age are relevant for our models
source(here("R", "func.R"))
#
#
var_m <- c("mit_density", "mit_potential", "ROS", "DNAdamage", "peroxidation")
formula_list_ <- list()
for (p in var_m){
  formula_list_[[p]] <- paste0(p, "~ cort*temp + age + sex + (1|clutch)")
  pmodel_name <- paste0("m_prel_", p)
  assign(pmodel_name, fit_m(df = clean_df,
                             cat = "prel",
                             var = p,
                             formula = formula_list_[[p]],
                             fam = gaussian(),
                             refit = FALSE),
          envir = .GlobalEnv)  # Assign to the global environment
}
#
#
# Run model behaviour (stimuli separated)
formula_learn <- slope_mean + slope_sd ~ cort*temp + age + sex + (1|clutch)
m_prel_learn <- fit_m(df = clean_df,
                      cat = "prel",
                      var = "slope_mean",
                      formula = formula_learn,
                      fam = gaussian(),
                      refit = FALSE)
```

@@

Table S4. Preliminary results of the models testing for ROS.
```{r, results_preliminary_ros}
#| tbl-cap: "Preliminary results of the models testing for ROS"
#| label: results_preliminary_ros
#
sum_m_ros_prel <- m_prel_ROS %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_ros_prel)
```

@@

Table S6. Preliminary results of the models testing for DNA damage.
```{r, results_preliminary_dnadamage}
#| tbl-cap: "Preliminary results of the models testing for DNA damage"
#| label: results_preliminary_dnadamage
#
sum_m_dnadamage_prel <- m_prel_DNAdamage %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_dnadamage_prel)
```

Model formula: DNAdamage ~ cort * temp + age + sex + (1|clutch).
Model convergence was checked through rhat and ess_bulk values. Summary indicates an effect of sex and age, so they were included in the final models.

@@

Table S8. Preliminary results of the models testing for lipid peroxidation.
```{r, results_preliminary_peroxidation}
#| tbl-cap: "Preliminary results of the models testing for lipid peroxidation"
#| label: results_preliminary_peroxidation
#
sum_m_peroxidation_prel <- m_prel_peroxidation %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_peroxidation_prel)
```

@@

>>>>

## Results

@@

```{r, models_mitochondrial}
#| label: models_mitochondrial
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# 
#
# Run models mitochondrial physiology 
var_m <- c("mit_density", "mit_potential", "ROS", "DNAdamage", "peroxidation")
for (p in var_m){ 
  if (p %in% c("mit_density", "mit_potential", "ROS", "DNAdamage")){
    formula <- paste0(p, "~ cort*temp + (1|clutch)")
  } else if (p == "peroxidation"){
    formula <- paste0(p, "~ cort*temp + age + (1|clutch)")
  } 
  pmodel_name <- paste0("m_def_", p)
  assign(pmodel_name, fit_m(df = clean_df,
                          cat = "def",
                          var = p,
                          formula = formula,
                          fam = gaussian(),
                          refit = FALSE),
        envir = .GlobalEnv)  # Assign to the global environment
} 
```

```{r, models_learning}
#| label: models_learning
#
formula_learn <- errors ~ day*cort*temp + (1 + day|lizard_id) + (1|clutch)
m_def_learn <- fit_m(df = learning_df,
                      cat = "def",
                      var = "learning",
                      formula = formula_learn,
                      fam = negbinomial(link = "log"),
                      refit = FALSE)
```

```{r, learning_results_names}
#| label: learning_results_names
# Rename some of the posteriors and make new estimates for the learning rate 
#
### Slopes
slope_ControlCold <- m_def_learn$b_day
slope_CORTCold <- m_def_learn$b_day + m_def_learn$`b_day:cortCORT`
slope_ControlHot <- m_def_learn$b_day + m_def_learn$`b_day:tempHot`
slope_CORTHot <- m_def_learn$b_day + m_def_learn$`b_day:cortCORT:tempHot` + m_def_learn$`b_day:cortCORT` + m_def_learn$`b_day:tempHot`
### Intercepts (for figure)
int_ControlCold <- m_def_learn$b_Intercept
int_CORTCold <- m_def_learn$b_Intercept + m_def_learn$`b_cortCORT`
int_ControlHot <- m_def_learn$b_Intercept + m_def_learn$`b_tempHot`
int_CORTHot <- m_def_learn$b_Intercept + m_def_learn$`b_cortCORT:tempHot` + m_def_learn$`b_cortCORT` + m_def_learn$`b_tempHot`
```

```{r, fig-learning}
#| label: fig-learning
#| fig.cap: "Learning results"
source(here("R", "func.R"))
#
#
####### A) Create df
# Slopes df (employed in fig-learning B)
slope_list <- list(`Control-Cold` = slope_ControlCold,
                 `CORT-Cold` = slope_CORTCold,
                 `Control-Hot` = slope_ControlHot,
                 `CORT-Hot` = slope_CORTHot)
data_fig_learning_slopes <- do.call(rbind, lapply(names(slope_list), function(x) {
  data.frame(treatment = x, slopes = slope_list[[x]])
}))
# Intercepst df (only for fig-learning A)
intercept_list <- list(`Control-Cold` = int_ControlCold,
                 `CORT-Cold` = int_CORTCold,
                 `Control-Hot` = int_ControlHot,
                 `CORT-Hot` = int_CORTHot)
data_fig_learning_intercepts <- do.call(rbind, lapply(names(intercept_list), function(x) {
  data.frame(treatment = x, intercepts = intercept_list[[x]])
})) %>% 
  group_by(treatment) %>%
  summarize(se_int = sd(intercepts)/sqrt(length(intercepts)),
            intercepts = mean(intercepts))
# df fig-learning A
data_fig_learning_slopesA <- data_fig_learning_slopes %>%
  group_by(treatment) %>%
  summarize(se_slope = sd(slopes)/sqrt(length(slopes)),
            slopes = mean(slopes),)
data_fig_learningB <- merge(data_fig_learning_slopesB, data_fig_learning_intercepts, by = "treatment")
treatment <- unique(data_fig_learningB$treatment)
fig_A_df <- data.frame()
for(t in treatment){ # Loop per treatment
  df <- data_fig_learningB %>%
    filter(treatment == t) %>%
    data.frame()
  # Variables selected
  m <- df$slopes
  u <- df$intercepts
  # Loop per treatment
  num_individuals <- length(u)
  for(x in 0:40){
    if (x == 0){
      standard <- df$se_int
    } else {
      standard <- df$se_slope
    }
    value <- exp(u + m * x)
    temp_df <- data.frame(trial = rep(x, length(value)),
                          treatment = rep(t, length(value)),
                          errors = value,
                          se = standard)
    fig_A_df <- rbind(fig_A_df, temp_df)
  }
}
# 
#### C) Plot the fig-learning A and fig-learning B separately 
fig_learningA <- plot_errors(fig_A_df)
fig_learningB <- plot_slopes(data_fig_learning_slopes)
#
#

errors_df <- data_spal %>%
  mutate(Treatment = paste(cort, temp, sep = "-")) %>%
    mutate(Treatment = factor(Treatment,
      levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
    )) %>%
  group_by(day, Treatment) %>%
  summarise(
    mean_errors = mean(errors, na.rm = TRUE),
    sd_errors = sd(errors, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  data.frame()
fig_errors <- ggplot(learn_df, aes(x = Trial, y = Value, color = Treatment, fill = Treatment)) +
  geom_smooth(se = TRUE, linewidth = 1, alpha = 0.075) +
  scale_color_manual(values = c("CORT-Cold" = "#00008B", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  scale_fill_manual(values = c("CORT-Cold" = "darkblue", "Control-Cold" = "#68bde1", "CORT-Hot" = "#b50101", "Control-Hot" = "#fa927d")) +
  theme_classic() +
  labs(y = "Mean amount of errors made", x = "Trial") +
  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
  theme(
    axis.title = element_text(size = 12, family = "Times"),
    axis.text = element_text(size = 10, family = "Times"),
    legend.position = "none"
  )
## B.2) Make the the plot for the mean slope per treatment using the probability of choosing the correct feeder
fig_slope_errors <- plot_slopes("errors")
#
#
## B.3) Combine plots of probability and slopes to have the "choice" figure
fig_results_errors <- plot_grid(fig_errors, fig_slope_errors, nrow = 1) 
ggsave("./output/figures/fig_results_errors.png", plot=fig_results_errors, width = 25, height = 15, units = "cm", dpi = 600)
```

# Suplementary Material

```{r, tbl-contrasts}
#| label: tbl-contrasts

@@

@@

#### Results of preliminary models

```{r, models_preliminary}
#| label: models_preliminary
# Fitting preliminary models to see if sex and age are relevant for our models
source(here("R", "func.R"))
#
#
var_m <- c("mit_density", "mit_potential", "ROS", "DNAdamage", "peroxidation")
formula_list_ <- list()
for (p in var_m){
  formula_list_[[p]] <- paste0(p, "~ cort*temp + age + sex + (1|clutch)")
  pmodel_name <- paste0("m_prel_", p)
  assign(pmodel_name, fit_m(df = clean_df,
                             cat = "prel",
                             var = p,
                             formula = formula_list_[[p]],
                             fam = gaussian(),
                             refit = FALSE),
          envir = .GlobalEnv)  # Assign to the global environment
}
#
#
# Run model learning including the effect of sex and interaction
formula_learn <- errors ~ day*cort*temp + sex + age + (1 + day|lizard_id) + (1|clutch)
m_prel_learn <- fit_m(df = learning_df,
                      cat = "prel",
                      var = "learning",
                      formula = formula_learn,
                      fam = negbinomial(link = "log"),
                      refit = FALSE)
```

@@

Table S3. Preliminary results of the models testing for ROS.
```{r, results_preliminary_ros}
#| tbl-cap: "Preliminary results of the models testing for ROS"
#| label: results_preliminary_ros
#
sum_m_ros_prel <- m_prel_ROS %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_ros_prel)
```

@@

Table S4. Preliminary results of the models testing for DNA damage.
```{r, results_preliminary_dnadamage}
#| tbl-cap: "Preliminary results of the models testing for DNA damage"
#| label: results_preliminary_dnadamage
#
sum_m_dnadamage_prel <- m_prel_DNAdamage %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_dnadamage_prel)
```

Model formula: DNAdamage ~ cort * temp + age + sex + (1|clutch).
Model convergence was checked through rhat and ess_bulk values. Summary indicates no effect of sex or age, so they were discarded from the final models.

@@

Table S5. Preliminary results of the models testing for lipid peroxidation.
```{r, results_preliminary_peroxidation}
#| tbl-cap: "Preliminary results of the models testing for lipid peroxidation"
#| label: results_preliminary_peroxidation
#
sum_m_peroxidation_prel <- m_prel_peroxidation %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_peroxidation_prel)
```

@@

Table S6. Preliminary results of the models testing for learning.
```{r, results_preliminary_learning}
#| tbl-cap: "Preliminary results of the models testing for lipid peroxidation"
#| label: results_preliminary_peroxidation
#
sum_m_learn_prel <- m_prel_learn %>%
  dplyr::select(starts_with("b_")) %>%  # Removes random effect terms
  summarise_draws() %>%
  mutate(across(where(is.numeric), ~ as.numeric(format_dec(.x, 3))))
#
flextable(sum_m_learn_prel)
```

Model formula: errors ~ day * cort * temp + sex + age+ (1 + day | lizard_id) + (1|clutch).
Model convergence was checked through rhat and ess_bulk values. **Summary indicates no effect of sex, so it was discarded from the final models. However, we saw an effect of age and we included it in our final models.**
